---
title: "Brownlows Bets"
author: "Sasha Sanchez"
date: "Summer 2021"
output: 
  html_document:
    number_sections: true
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
require(knitr)
source(file= "BrLw.R")
```


<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

 At the first day of class there are 35 students in Math Statistics class and professor Brownlow always proposes this bet to his students "I will wager $2 to your bet of $1 that at least two people in today's class have  the same birthday.  He tells me he has made that bet 637 times so far. Where do you think his profits are? Discuss this in a markdown document
 
Report git commit structure:
There are 3 questions and there should be at least 3 separate commits, at least one dealing with each of the 3 questions.
1. What are the fair odds for a bet on matching birthdays in a 35 person class.
2. For what size class is a 2:1 odds bet fair.
3. How much money would Brownlow be expected to end up with if the bets went as described.

# What are the fair odds  


<!--Decide on your methods:  In this section explain the approach you will take to attack the issue --- how will you decide on a likely estimate of professor Brownlow's earnings or losses after 637 bets. Also explain how you construct a 95% confidence interval about your estimate of his winnings !-->

```{r}
BrLw(35,4.35,637)
```



```{r}
bank=numeric()
for(j in 1:500){
  


bank[j] = BrLw(35,4.35,637)}
```


```{r}
hist(bank)
favstats(bank)
arranged<-sort(bank)
print(arranged[12])
print(arranged[488])
```

The number of Brownlows would have to bet $4.35. The way to tell is by the 0 that is in the middle by that it has reached fair odds. We can also see that the 'MIN' is -176 which means we can either win or lose money.



# What size of class makes the 2:1 bet fair?  
<!--Explain and display the results of your method of coming up with the estimate of professor Brownlows betting profits!-->




```{r}
BrLw(35,2,637)
```



```{r}
bank=numeric()
for(j in 1:1000){
  


bank[j] = BrLw(35,2,637)}
```



```{r}
hist(bank)
favstats(bank)
arranged<-sort(bank)
print(arranged[25])
print(arranged[975])
```

In this histogram we can see that the 0 shifted to the left side making it a little harder to win money. We can see that the 'MIN' is -188 again give or take win or losing money. 


# In the class and payoff as described what is a 95% confidence interval for Brownlow's earnings?
  
<!--Explain and display your method of coming up with a 95% confidence interval of  professor Brownlows winnings (or losings)-->


```{r}
BrLw(29,2,637)
```


```{r}
bank=numeric()
for(j in 1:1000){
  


bank[j] = BrLw(29,2,637)}
```



```{r}
hist(bank)
favstats(bank)
arranged<-sort(bank)
print(arranged[12])
print(arranged[488])
```

Now we have seen that the 0 is in the middle so that leaves this to be fair odds. On winning or losing money. The 'MIN' is -92 in this histogram. 

We going to try this 1000 times to see if we can get a 95% confidence interval. We are going to sort this out from low to high so that the middle can be 95%.


# Discussion and Conclusion

<!--Discussion and conclusion here.  If professor Brownlow is consistantly making or losing money how could he change his payout so that his profits center on zero?  Also discuss what size his class should be in order to have his current scheme balance at zero profit.!-->


Given the graphs above we can see that there is a differences when we plug in different numbers, The numbers are always going to change statistically speaking. We plugged in different numbers to see if we can tell which graph is much more better. The graphs that had the zero in the middle would be more better given that the chances are fair odds. 



